Toward \earlywarning\ detection of gravitational waves from compact binary coalescence

### 2012-04-04 article.tex
Added commas
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@1511 ccdd05d5-56c1-461a-bf98-85f6876523b4

Table~\ref{table:flops} shows that the \lloid\ method requires $6.6 \times 10^8$
\flops\ to cover a sub-bank comprising 657 out of the total 98544 mass pairs.
Assuming that other regions of the parameter space have similar computational
scaling, an entire single-detector search for \NS--\NS\ signals in the
1--3~$M_\odot$ component mass range could be implemented with $(98544/657)\approx150$ times the cost, or $9.9 \times 10^{10}$~\flops.

>>>>

Table~\ref{table:flops} shows that the \lloid\ method requires $6.6 \times 10^8$
\flops\ to cover a sub-bank comprising 657 out of the total 98,544 mass pairs.
Assuming that other regions of the parameter space have similar computational
scaling, an entire single-detector search for \NS--\NS\ signals in the
1--3~$M_\odot$ component mass range could be implemented with $(98,544/657)\approx150$ times the cost, or $9.9 \times 10^{10}$~\flops.
